---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dshr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/feralaes/dshr.svg?branch=master)](https://travis-ci.org/feralaes/dshr)
<!-- badges: end -->

An R package that implements the methods to derive disease-specific hazard ratios (dsHR) from overall hazard ratios (oHR) described in the publication: 

- Alarid-Escudero F, Kuntz KM "Potential bias associated with modeling the effectiveness of healthcare interventions in reducing mortality using an overall hazard ratio" 2019 (Under review)

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("feralaes/dshr")
```
## Example

This is a basic example which shows you how to derive a disease-specific hazard ratio (dsHR) from a disease-specific mortality rate, an overall hazard ratio (oHR) reported in a trial, the initial age of the cohort in the trial, and the length of the trial using an empirical approach with background mortality from US life tables.

```{r example, message=FALSE, warning=FALSE}
library(dshr)
ohr        <- 0.55 # Overall hazard ratio (oHR)
n_age_init <- 50   # Initial age of cohort in trial
trial_time <- 5    # Length of clinial trial in years
mu_Dis     <- 0.05 # Disease-specific mortality rate

dshr_emp <- calc_dshr_from_ohr(ohr = ohr, 
                               mu_Dis = mu_Dis,
                               n_age_init = n_age_init, 
                               trial_time = trial_time, 
                               hazard = "empirical")
dshr_emp
```
